Viscous Erosion in Porous Media

### 2018-03-04 docs/methods/erosion_methods.tex
NM

With the shear stress computed, we are now ready to numerically evolve the boundaries using the {\thL} framework. The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.  In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law \eqref{eqn:Vn}. This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1} for $\theta(\alpha,t)$. For numerical stability, we will treat the stiff term with an exponential integrator, while handling all other terms in \eqref{eqn:Levo1}--\eqref{eq:xsurf} with an explicit Runge-Kutta method. Ultimately, we will arrive at a method that is second-order in time.

>>>>

With the shear stress computed, we are now ready to numerically evolve the boundaries using the {\thL} framework. The main equations to be solved are \eqref{eqn:Levo1}--\eqref{eq:xsurf}.  In Section~\ref{sec:thetaL} we introduced a curvature-penalizing term into the erosion law \eqref{eqn:Vn}. This term suppresses high-frequency oscillations, but also introduces {\em stiffness} into evolution equation \eqref{eqn:thetaevo1}. We will therefore use a combined exponential-integrator/Runge-Kutta method to solve system \eqref{eqn:Levo1}--\eqref{eq:xsurf}. The exponential integrator will handle the stiff term in a numerically stable fashion, while the Runge-Kutta method will treat the nonlinear terms explicitly. Our overall time-stepping method will be second order.
